%!TEX TS-program = xelatex
\documentclass[]{./friggeri-coverletter}
\usepackage{sourcesanspro}

\personalinfo{Gerald}%
	     {Brown}%
	     {274 E Saint John St, Apt 2}%
	     {San Jose, CA 95112}

% in format {mr./ms./etc.}{first}{last}{position}
\contact{}%
	{}%
	{}%
	{}

% in format {organization name}{street addr}{city, state zip}
\address{IBM}%
	{555 Bailey Avenue}%
	{San Jose, CA 95141}

\begin{document}
\letterheader%
% %%%%%%%%%%%%%%%%%%%% PARAGRAPH ONE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%% Relevance to position, passion for wanting to work there (personal story)
%
% State the reason for the letter, name the position or type of
% work you are applying for and identify the source from which
% you learned of the opening.
%
% Opening paragraph: Statement of Purpose
% Open with a captivating introductory sentence, name the position you're
% applying for, and how you learned about the position.
\begin{bp}
I enjoy scripting. As a person who wrote a script for the sake of making this
cover letter's formatting a little less time-consuming, I should. That is, in
part, why I'm writing you now. I came across the opening for Software
Engineer Intern while searching LinkedIn for an internship that would be a fit
for me. By the end of this letter, I hope to make a pretty convincing case for
why I'd be a good fit for the position, as well.
\end{bp}%
% %%%%%%%%%%%%%%%%%%%% PARAGRAPH TWO %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Indicate why you are interested in the position, the company,
% its products, services - above all, stress what you can do for
% the employer. If you are a recent graduate, explain how your
% academic background makes you a qualified candidate for the
% position. If you have practical work experience, point out
% specific achievements or unique qualifications. Try not to
% repeat the same information the reader will find in the resume.
% The purpose of this section is to strengthen your resume by
% providing details which bring your experiences to life.
%
% Middle paragraph(s): Explanation of Qualifications
% Part 1: Write about why you're applying to this organization. Include the
% organization's purpose and/or goals and how the position relates to them.
% Part 2: Explain why you're a great candidate for the position. List the 
% reasons you're interested in the position and how your relevant skills will 
% allow you to fulfill the responsibilities in the job description.
\begin{bp}
The opportunity to contribute to a company doing innovative,
challenging work while holding itself to high societal standards has been one 
of my primary concerns with searching for an internship. With its involvement
in the first landing on the moon through to creating the Jeopardy-winning 
Watson of present day, ``Big Blue'' has managed to check all of these boxes
off. To work with the company that holds the distinction of having started
artifical intelligence research, and to still be doing that research today, is
impressive. I'm also aware that IBM has been recognized for hiring the first
female vice president and the first black salesman -- all prior to 1950. To do
any work that even indirectly supports these causes would be infinitely
rewarding.
\end{bp}
\begin{bp}During my day-to-day, I primarily work in Unix and have had some
experience with servers and retrieving information in both XML and JSON
formats. I'm beginning to work with AWS, but my overall experience is 
limited. As a result of performing especially well in an Operating Systems
course, I am now an undergraduate researcher at UCSC's Storage Systems Research
Center, where distributed systems, deduplication, and security are active areas
of research. With this internship, I hope to make substantial contributions to 
IBM, to determine within what area my research should fall, and, most of all,
to learn.
\end{bp}
% %%%%%%%%%%%%%%%%%%%% PARAGRAPH THREE %%%%%%%%%%%%%%%%%%%%%%%%%%
% Request a personal interview and indicate your flexibility as to
% the time and place. Repeat your phone number in the letter. End
% letter by thanking the employer for taking the time to consider
% your credentials.
%
% Closing paragraph: Conclusion
% Begin with one or two strong lines that summarize your qualifications,
% thank the reader for their consideration, and express your enthusiasm
% about meeting with them to discuss the opportunity.
\begin{bp}
I thank you for your consideration. At your earliest convenience, please
contact me at 408-807-8277, or any of the other methods listed on my resume
and website, if you would like to discuss this position further.
\end{bp}
\closing%
\end{document}
