%!TEX TS-program = xelatex
\documentclass[]{./friggeri-cv}
\usepackage{sourcesanspro}

\begin{document}
\header{gerald}{brown}
       {github contributor}

% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    \hspace{-3em}555 Sugarloaf Rd
    Sunny, CA 90210 
    ~
    {Cell Phone: 555-555-5555} 
    ~ 
    E-Mail:
    \href{mailto:email@domain.com}{\hspace{-3em}email@domain.com}
    ~
%    \linespread{1.5}\href{https://www.facebook.com/gerald.m.brown}{fb://gerald.m.brown}% 
%    ~
    URL: \href{http://www.iamprofessional.com}{notaprofessional.com}
    ~ 
    LinkedIn:\hspace{-1em} \href{http://linkedin.com/in/thisguy}{\hspace{-3em}linkedin.com/in/yourprofile}
    ~
    GitHub: \href{http://www.github.com/gemabrow}{\hspace{-3em}www.github.com/gemabrow}
  \section{proficient in}
    \LaTeX
   {\color{red} $\varheartsuit$} %
    Linux, Git
    Java
    C, C\#
    XML, XAML
    CSS3 \& HTML5
    Google Maps SDK
  \section{familiar with}
    Bootstrap 
    C++
    Prolog
    Python
    Haskell
    JavaScript
    (VG, Raphael, jQuery)
\end{aside}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{education}
\begin{entrylist}
  \entry
    {2017}
    {B.Sc. {\normalfont Computer Science}}
    {Your University}
    {Additional Info} 
\end{entrylist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{coursework}
%Algorithm Design, %
%Computational Modeling, %
%Computer Systems \& Assembly Language, %
%Computer Architecture, %
%Discrete Mathematics, %
%Introduction to Artificial Intelligence, % 
%Operating Systems, %
%Probability Theory, %
%Software Engineering. %
%Vector Calculus. %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{experience}
\begin{entrylist}
\entry
    {2006 -- 2013}
    {\href{http://wisequacks.org/wp2/wp-content/uploads/2012/05/coffee.jpg}{Starbucks Coffee Company}}
    {Sunny, CA}
    {{\rolefont Barista.}\\Recognized for speed of service and an infectious smile.
    Repeatedly part of shifts responsible for scoring 93\%-100\% on audits of
    cleanliness, customer service, and food \& beverage preparation.}
\end{entrylist}\vspace{-1.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{projects}%
\begin{entrylist}
  \entry
    {2016}
    {SlugLife}
    {\href{https://sites.google.com/a/ucsc.edu/sluglife/}{project page}}
    {Android/iOS application which tracks UCSC campus shuttles and
    communicates with several databases to provide shuttle locations, upcoming
    events, occupancy of gym facilities, and more.}
%   \entry
%     {2014}
%     {We Bus}
%     {\href{https://www.youtube.com/watch?time\_continue=1&v=8qLESklGc3s}{youtube demo}}
%     {Android application concept which provided Santa Cruz Metro transit riders real-time bus locations and projected arrival times.}
%  \entry
%    {2014}
%    {Tag!}
%    {\href{https://docs.google.com/presentation/d/1XygoBYkCEAtTAAr2VJopf0PE37B%
%    ENOvAQkDNCBz3WPI/pub?start=false\&loop=false&delayms=3000\&slide=id.p}{presentation}}
%    {Web-based application for Stanford University's Visual Genome project which gamified crowdsourced image-tagging.}
\end{entrylist}\vspace{-1.5em}
\section{recognition}
    {\href{http://honors.ucsc.edu/awards/dca/index.html}{\bf Dean's Award}}\\
    Credited for contributions to SlugLife project, winner of
    2016 -- 2017 UCSC Baskin School of Engineering Dean's Award for outstanding
    undergraduate achievement.%
    \newline\\
    {\href{http://isee.ucsc.edu/programs/west/index.html}%
    {\bf Workshops for Engineering and Science Transfers (WEST)}}\\
    {Selected for participation. Presented findings from applying 
    engineering methods to fundamental concepts in hydrodynamics and 
    water-driven power generation.}
\end{document}
