%!TEX TS-program = xelatex
\documentclass[]{./friggeri-cv}
\usepackage{sourcesanspro}

\begin{document}
\header{gerald}{brown}
       {c.s. student}

% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    \hspace{-3em}274 E Saint John St, Apt 2
    San Jose, CA 95112
    ~
    {Cell Phone: 408-807-8277} 
    ~ 
    E-Mail: \href{mailto:geraldbrown@geraldcodes.com}{\hspace{-5em}geraldbrown@geraldcodes.com}
    ~
    %\linespread{1.5}\href{https://www.facebook.com/gerald.m.brown}{fb://gerald.m.brown}% 
    URL: \href{http://www.geraldcodes.com}{www.geraldcodes.com}
    ~ 
    LinkedIn: \href{http://linkedin.com/in/geraldcodes}{\hspace{-3em}linkedin.com/in/geraldcodes}
    ~
    GitHub: \href{http://www.github.com/gemabrow}{\hspace{-3em}www.github.com/gemabrow}
  \section{proficient in}
    \LaTeX
   {\color{red} $\varheartsuit$} %
    *nix, Git
    Java
    C, C\#
    XML, XAML
    CSS3 \& HTML5
    Google Maps SDK
 \section{familiar with}
    C++
    Prolog
    Python
    Haskell
    JavaScript
    (VG, Raphael, jQuery)
\end{aside}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{education}
\begin{entrylist}
  \entry
    {2013 -- present}
    {B.Sc. {\normalfont Candidate, expected March 2016}}
    {University of California, Santa Cruz}
    {Majoring in Computer Science}
  \entry
    {2010 -- 2013}
    {Associate's. cum laude}
    {Merced Community College}
    {\emph{Faculty-Selected Honors} A.S. in Computer Science,
    \\A.A. in Engineering, A.S.T. in Mathematics, A.S. in Physics}
\end{entrylist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{coursework}
Algorithm Design, %
Computational Modeling, %
Computer Systems \& Assembly Language, %
Computer Architecture, %
Discrete Mathematics, %
Introduction to Artificial Intelligence, % 
Operating Systems, %
Probability Theory, %
Software Engineering, %, %
Vector Calculus. %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{experience}
\begin{entrylist}
\entry
    {2016 -- present}
    {\href{http://www.ssrc.ucsc.edu/index.html}{Storage Systems Research Center%
    , Jack Baskin School of Engineering}}
    {Santa Cruz, CA}
    {{\rolefont Student Researcher.}\\Performing investigative research for a
    research proposal pertinent to archival storage, large-scale distributed
    storage systems, or security and reliability in storage systems.}
%\\\entry
%     {2013 -- 2014}
%     {\href{http://arboretum.ucsc.edu/}{The Arboretum}}
%     {Meet-and-Greeter}
%     {Increased admission sales and provided a congenial atmosphere to
%     fellow employees and patrons.}% \\\entry
%    {01 - 03 2014}
%    {\href{http://projectclearinghouse.ucsc.edu/microgrid-sensor-design%
%-localized-climate-data-research}%
%{Engineering and Sustainability through Student Service}}
%    {Santa Cruz, CA}
%    {\emph{Research Internship.}\\ Executed production of arduino-based weather stations as a viable non-commercial option.}
\entry
    {2012 -- 2013}
    {\href{http://www.mccd.edu/resources/tutoring/tutorial-center.html}{Merced Community College Tutorial Center}}
    {Merced, CA}
    {{\rolefont Tutor.}\\Utilized adaptive communication skills to engender students'
    success in Computer Science, Mathematics, and English courses. Specifically 
    requested for services by several students of varying demographics.}
\entry
    {2006 -- 2013}
    {\href{http://wisequacks.org/wp2/wp-content/uploads/2012/05/coffee.jpg}{Starbucks Coffee Company}}
    {Merced, CA}
    {{\rolefont Barista.}\\Recognized for speed of service and an infectious smile.
    Repeatedly part of shifts responsible for scoring 93\%-100\% on audits of
    cleanliness, customer service, and food \& beverage preparation.}
\end{entrylist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{projects}
\begin{entrylist}
  \entry
    {2016}
    {\href{https://sites.google.com/a/ucsc.edu/sluglife/}{SlugLife}}
    {}
    {Android/iOS application which tracks UCSC campus shuttles and
    communicates with several databases to provide shuttle locations, upcoming
    events, occupancy of gym facilities, and more.}
%   \entry
%     {2014}
%     {We Bus}
%     {\href{https://www.youtube.com/watch?time\_continue=1&v=8qLESklGc3s}{youtube demo}}
%     {Android application concept which provided Santa Cruz Metro transit riders real-time bus locations and projected arrival times.}
%  \entry
%    {2014}
%    {Tag!}
%    {\href{https://docs.google.com/presentation/d/1XygoBYkCEAtTAAr2VJopf0PE37B%
%    ENOvAQkDNCBz3WPI/pub?start=false\&loop=false&delayms=3000\&slide=id.p}{presentation}}
%    {Web-based application for Stanford University's Visual Genome project which gamified crowdsourced image-tagging.}
\end{entrylist}
\section{recognition}
    {\href{http://honors.ucsc.edu/awards/dca/index.html}{\bf Dean's Award}}\\
    Credited for contributions to SlugLife project, winner of
    2016 -- 2017 UCSC Baskin School of Engineering Dean's Award for outstanding
    undergraduate achievement.%
%    \newline\\
%    {\href{http://isee.ucsc.edu/programs/west/index.html}%
%    {\bf Workshops for Engineering and Science Transfers (WEST)}}\\
%    {Selected for participation. Presented findings from applying 
%    engineering methods to fundamental concepts in hydrodynamics and 
%    water-driven power generation.}
\end{document}
